---
title: 'Statistical report: Quality indicators for heart failure: a validation study using nationwide registry data – a SwedeHF study'
subtitle: 'DRAFT'
author: 'Statistician: Lina Benson'
  
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    number_sections: yes
link-citations: yes
bibliography: references.bib
nocite: '@*'
urlcolor: blue
linkcolor: black
header-includes:
   - \usepackage{subfig}
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}
---

\newpage 
\tableofcontents 
\listoftables
\listoffigures
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, include = TRUE, comment = "",
  warning = FALSE, message = FALSE, fig.pos = "H",
  fig.path = "../output/figs/"
)
options(knitr.kable.NA = "")
```

```{r adjust_directory_if_needed, include=FALSE}
# Uncomment lines below if rmd file is placed in a subdirectory
knitr::opts_knit$set(root.dir = normalizePath("../"))
```

```{r load_project}
# 1. Set options in config/global.dcf
# 2. Load packages listed in config/global.dcf
# 3. Import functions and code in lib directory

ProjectTemplate::reload.project()

cacheon <- TRUE
```             

# Data handling

## Data source

The same raw data as SHFDB3, https://kiheartfailure.github.io/shfdb3/. In order to include patients up until 2019-12-31 the data management 
was however performed separately for this analyses. 

## Inclusion/exclusion criteria

```{r flow}
default_kable(flow, caption = "Flowchart")
```

First patient in: `r min(rsdata$shf_indexdtm)` and last patient in: `r max(rsdata$shf_indexdtm)`.  

The median age (IQR) is `r rsdata %>% summarise(med = fn(median(shf_age), dig = 1),
                                             q1 = fn(quantile(shf_age, probs = 0.25), dig = 1),
                                             q3 = fn(quantile(shf_age, probs = 0.75), dig = 1)) %>%
                                   mutate(out = paste0(med, " (", q1, "-", q3, ")")) %>%
                                   pull(out)` and 
`r rsdata %>% count(shf_sex) %>%
  mutate(perc = fn(n / sum(n) * 100, 1)) %>%
  filter(shf_sex == "Female") %>%
  pull(perc)`% females.    

There were `r rsdata %>% group_by(shf_centre) %>% slice(1) %>% nrow()` centers with 
  `r rsdata %>% count(shf_centre) %>% summarise(med = fn(median(n), dig = 1),
                                             q1 = fn(quantile(n, probs = 0.25), dig = 1),
                                             q3 = fn(quantile(n, probs = 0.75), dig = 1)) %>%
                                   mutate(out = paste0(med, " (", q1, "-", q3, ")")) %>%
                                   pull(out)` patients.      

## Created variables 

```{r npr}
default_kable(metaout, caption = "Outcomes and comorbidities from NPR")
```

```{r ddr}
default_kable(metalm, caption = "Medications from DDR")
```

## Definition of QI variables

```{r codecreateqi, code = readLines("../munge/12-qivars.R"), echo = TRUE, eval = FALSE}

```

Note that the EF QI is removed from the opportunity based scores.

### Sensitivity analysis

For the CRT and ICD QI a sensitivity analysis was performed including patients with EF <40% instead of <30% and 
not applying the ECG (for CRT) and NYHA class criteria. 

# Statistical analysis 

## General

All analyses were performed using `r sessionInfo()$R.version$version.string` [@r]. 
The level of significance is set to 5%, two-sided. No adjustment for multiple 
comparisons were made and therefore the results should be viewed with some care.

## Centre

All analyses on centre variation include only centres => 10 patients for the respective analyses. 

## Missing data

Missing data was imputed with multiple imputation (n = 10) using mice [@mice] 
for the multivariable logistic and Cox regression models. 
Variables included in the model are indicated in 
Table \ref{tab:tab1}. All-cause mortality was included as the Nelson-Aalen estimator. 
The QI were not imputed and based on non-imputed raw data. 

## Baseline characteristics

```{r, child = "../src/tab1.Rmd"}

```

## Feasibility and attainment assessment

```{r, child = "../src/feasability.Rmd"}

```

\clearpage

The likelihood of attainment is assessed using a logistic regression, crude and adjusted for the variables indicated in 
Table \ref{tab:tab1}. (the generalized linear mixed-effects model
(GLMM) with a logit link and a random effect for centre just took too long for this amount of models, observations, variables and imputations)

```{r, child = "../src/logreg.Rmd"}

```

\clearpage

```{r, child = "../src/corr.Rmd"}

```

```{r, child = "../src/boxplot.Rmd"}

```

\clearpage

## Outcome analysis

The following outcomes are considered at 1 year and for whole follow-up period: 

- All-cause mortality (primary outcome)
- Composite of CV mortality/First Heart failure hospitalization (HFH)
- CV mortality
- First Heart failure hospitalization (HFH)

Data were censored at 2019-12-31, death (for the outcome HFH) or emigration from Sweden. 

The outcomes were presented with Kaplan-Meier plots. Cox proportional hazards regressions with a
frailty term for centre were used to model the time to first event. Variables included in the model are indicated in 
Table \ref{tab:tab1}. Adjustment is not performed for variables that are included in the calculation of the QI 
(i.e, for qi ef, ef is not adjusted for, for qi lab, anemia and eGFR is not adjusted for...). 

The median (min-max) follow-up is 
`r rsdata %>% summarise(med = fn(median(sos_outtime_death / 365.25 * 12), dig = 1),
                                             min = fn(min(sos_outtime_death / 365.25 * 12), dig = 1),
                                             max = fn(max(sos_outtime_death / 365.25 * 12), dig = 1)) %>%
                                   mutate(out = paste0(med, " (", min, "-", max, ")")) %>%
                                   pull(out)` months for a total of 
                                   `r rsdata %>% summarise(sumpy = fn(sum(sos_outtime_death) / 365.25, dig = 0)) %>%
                                   pull(sumpy)` patient-years of follow-up.

### Assumptions

TO DO: The proportional hazards assumption was investigated using the scaled Schoenfeld 
residuals (cox.zph in [@survival-package]) for the primary outcome. 
Possible outliers were visually inspected by plotting the dfbetas. 
=> XXXX. Also check liniearity ect. 

```{r, child = "../src/outtab.Rmd"}

```

\clearpage

```{r, child = "../src/km.Rmd"}

```

\clearpage
\newpage

# Reproducibility

## R session information {#sessioninfo}

```{r sessinfo}
sessionInfo()
```

## R code

The R code for all data handling and statistical analyses are found: 
https://github.com/KIHeartFailure/validation_qi. On publication
the repository will be made public so as to 
link to it from the resulting article for increased transparency and code sharing.
No data or output is stored in the repository. 

# References