---
title: 'Statistical report: Quality indicators for heart failure: a validation study using nationwide registry data – a SwedeHF study'
subtitle: 'DRAFT'
author: 'Statistician: Lina Benson'
  
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    number_sections: yes
link-citations: yes
bibliography: references.bib
nocite: '@*'
urlcolor: blue
linkcolor: black
header-includes:
   - \usepackage{draftwatermark}
---

\newpage 
\tableofcontents 
\listoftables
\listoffigures
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, include = TRUE, comment = "",
  warning = FALSE, message = FALSE, fig.pos = "H",
  fig.path = "../output/figs/"
)
options(knitr.kable.NA = "")
```

```{r adjust_directory_if_needed, include=FALSE}
# Uncomment lines below if rmd file is placed in a subdirectory
knitr::opts_knit$set(root.dir = normalizePath("../"))
```

```{r load_project}
# 1. Set options in config/global.dcf
# 2. Load packages listed in config/global.dcf
# 3. Import functions and code in lib directory

ProjectTemplate::reload.project()

cacheon <- TRUE
```             

# Data handling

## Data source

The same raw data as SHFDB3, https://kiheartfailure.github.io/shfdb3/. In order to include patients up until 2019-12-31 the data management 
was however performed separately for this analyses. 

## Inclusion/exclusion criteria

```{r flow}
default_kable(flow, caption = "Flowchart")
```

First patient in: `r min(rsdata$shf_indexdtm)` and last patient in: `r max(rsdata$shf_indexdtm)`.  

The median age (IQR) is `r rsdata %>% summarise(med = fn(median(shf_age), dig = 1),
                                             q1 = fn(quantile(shf_age, probs = 0.25), dig = 1),
                                             q3 = fn(quantile(shf_age, probs = 0.75), dig = 1)) %>%
                                   mutate(out = paste0(med, " (", q1, "-", q3, ")")) %>%
                                   pull(out)` and 
`r rsdata %>% count(shf_sex) %>%
  mutate(perc = fn(n / sum(n) * 100, 1)) %>%
  filter(shf_sex == "Female") %>%
  pull(perc)`% females.    

There were `r rsdata %>% group_by(shf_centre) %>% slice(1) %>% nrow()` centers with 
  `r rsdata %>% count(shf_centre) %>% summarise(med = fn(median(n), dig = 1),
                                             q1 = fn(quantile(n, probs = 0.25), dig = 1),
                                             q3 = fn(quantile(n, probs = 0.75), dig = 1)) %>%
                                   mutate(out = paste0(med, " (", q1, "-", q3, ")")) %>%
                                   pull(out)` patients.      

## Created variables 

```{r npr}
default_kable(metaout, caption = "Outcomes and comorbidities from NPR")
```

## Definitions of QI variables

Not an easy read, sorry, can help to "translate" into words if needed. 

NOTE: Made changes to the ICD definition (so more in line with CRT). 

Note that loop diuretic includes BOTH pats prescribed daily or when needed (however not IV). OK?

```{r codecreateqi, code = readLines("../munge/11-qivars.R"), echo = TRUE, eval = FALSE}

```

I grouped the op based scores into a categorical variable as well, for presentational purposes in for example KM plots. 
(note that the scores won't take even numbers for example 1-6, but pretty much on a continuous scale). 
Let me know if you prefer other cut-offs.

# Statistical analysis 

## General

All analyses were performed using `r sessionInfo()$R.version$version.string` [@r]. 
The level of significance is set to 5%, two-sided. No adjustment for multiple 
comparisons were made and therefore the results should be viewed with some care.

## Centre

All analyses on centre variation include only centres => 10 patients for the respective analyses. 

## Missing data

Missing data was imputed with multiple imputation (n = 10) using mice [@mice] 
for the multivariable Cox regression models. 
Variables included in the model are indicated in 
Table \ref{tab:tab1}. All-cause mortality was included as the Nelson-Aalen estimator. 
The QI were not imputed and based on non-imputed raw data. 

## Baseline characteristics

```{r, child = "../src/tab1.Rmd"}

```

## Feasibility and attainment assessment

```{r, child = "../src/feasability.Rmd"}

```

\clearpage

The likelihood of attainment is assessed using a generalized linear mixed-effects model
(GLMM) with a logit link and a random effect for centre. 

```{r, child = "../src/logreg.Rmd"}

```

You wanted to remove the tab Likelihood of attainment, please do if you see fit. 
This is basically the same info as in Tab \ref{tab:tabqibyvars} but also tested for stat sig (and with an effect measure). 
Could also look at more variables (in a forestplot) but then you would have one 
forestplot for each qi so think perhaps better just to look at these 4 variables and keep it simple? 

Currently the OR are unadjusted but could adjust, but not sure it would add info you want?

\clearpage

Let me know what (abbreviated) names you want in the corr plot (also for other plots). 

Note the definition of CRT (to be in the denominator you need a measure on ecg so 
per definition all patients with missing ecg will NOT fulfil the crt qi), 
so the high correlation between crt and ecg is probably in large part due to 
the definition of the qi (so basically not a true clinical corr, but a data technicality). 

```{r, child = "../src/corr.Rmd"}

```

```{r, child = "../src/boxplot.Rmd"}

```

\clearpage

## Outcome analysis

The following outcomes are considered: 

- All-cause mortality
- First Heart failure hospitalization (HFH)

Data were censored at 2019-12-31, death (for the outcome HFH) or emigration from Sweden. 

The outcomes were presented with Kaplan-Meier plots. Cox proportional hazards regressions with a
frailty term for centre were used to model the time to first event. Variables included in the model are indicated in 
Table \ref{tab:tab1}. Adjustment is not performed for variables that are included in the calculation of the QI 
(i.e, for qi ef, ef is not adjusted for, for qi lab, anemia and eGFR is not adjusted for...). 

The median (min-max) follow-up is 
`r rsdata %>% summarise(med = fn(median(sos_outtime_death / 365.25 * 12), dig = 1),
                                             min = fn(min(sos_outtime_death / 365.25 * 12), dig = 1),
                                             max = fn(max(sos_outtime_death / 365.25 * 12), dig = 1)) %>%
                                   mutate(out = paste0(med, " (", min, "-", max, ")")) %>%
                                   pull(out)` months for a total of 
                                   `r rsdata %>% summarise(sumpy = fn(sum(sos_outtime_death) / 365.25, dig = 0)) %>%
                                   pull(sumpy)` patient-years of follow-up.

I didn't do the caterpillar plot you requested. If the focus of the paper is feasibility and validation of the QI, and since the 
fig does not include the QI, I think it will just dilute the message and be a bit confusing. 
There is centre presentation in the baseline tab and qi tabs but I think this is much less "dominant". We had this discussion at our meeting, how much focus should be put on the centre variation 
(or should leave for another paper), regarding the BMJ method. Perhaps decide on the focus first? 

Note that in the data there are BOTH in and out-patients. Does this make it difficult to interpret? 
For example lab values are more common in in-patients so the association between 
labs taken and outcomes could perhaps be an effect of this? Restrict analyses to either in or out-pats? Stratify also outcome analyses by in and out-patients? 

Some models did not converge (the odd looking ones with ridiculously large CI), will remove from output later, for now just disregard. 

I think maybe a better presentation is needed to highlight some of the numbers in the cox regression table? 
Perhaps choose one time point (6mo or long-term) and present the adj numbers in forestplots (one for all-cause mort and one for hfh) 
and place the complete tab in supplements?

### Assumptions

TO DO: The proportional hazards assumption was investigated using the scaled Schoenfeld 
residuals (cox.zph in [@survival-package]) for the primary outcome. 
Possible outliers were visually inspected by plotting the dfbetas. 
=> XXXX. Also check liniearity ect. 

```{r, child = "../src/outtab.Rmd"}

```

\clearpage

```{r, child = "../src/km.Rmd"}

```

\clearpage
\newpage

# Reproducibility

## R session information {#sessioninfo}

```{r sessinfo}
sessionInfo()
```

## R code

The R code for all data handling and statistical analyses are found: 
https://github.com/KIHeartFailure/validation_qi. On publication
the repository will be made public so as to 
link to it from the resulting article for increased transparency and code sharing.
No data or output is stored in the repository. 

# References